Setting up Data

### 2019-12-03 src/SetupData.Rmd
re-ran with updated AnonData file

The original dataset contains the quantification batches

@@

Settting up main data file with explanation and examination of data.  Make the raw original DF and main working DF with bad cells exlcuede.  (inline code add the numbers)

There are `r length(original_DF_duplicates$fileName)` duplicated file names. These data will be used to quantify repeatability, and remove from the final DFs.
Using the distinct() function for the MLH1_data, the first duplicated filename is kept and the second removed.

@@

```{r save.RData, echo=FALSE}

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_12.3.19.RData")

#  OutPut: big large MLH1_data (AP's) df, big DF of BD with just the mice I want.
#  MLH1_data_table, means and variance of AP and BD MLH1 values. made from seperate tables from AP and BD data.
#  make sure decimal places are consistant

>>>>

All images were manually quantified after the file name was anonimized. The original (full) dataset contains the quantification batches with the following number of images. Each batch csv file was merged into Anon.csv by hand.

@@

The original dataset was cleaned up in the following ways before analysis. Settting up main data file with explanation and examination of data. Make the raw original DF and main working DF with bad cells exlcuede. The original dataset had `r length(original_DF_duplicates$fileName)` duplicated file names. These were removed and can be used to quantify repeatability or repair. Using the distinct() function for the MLH1_data, the first duplicated filename is kept and the second removed.

@@

```{r save.RData, echo=FALSE}
save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_12.3.19.RData")
#  OutPut: big large MLH1_data (AP's) df, big DF of BD with just the mice I want.
#  MLH1_data_table, means and variance of AP and BD MLH1 values. made from seperate tables from AP and BD data.
#  make sure decimal places are consistant
